Roster Review (Generic)

### 2019-04-26 rosterReview_generic.Rmd
A touch of refactoring/organizing

```{r}
filename <- function(name) {
  paste0("data/",name,"_",gsub("-","",Sys.Date()),".Rds")
}

draft_results <- read_tsv("data/draftResults.tsv") %>% 
    clean_names() %>% 
    mutate(player = stri_trans_general(player, "latin-ascii")) %>% 
    select(pick, player)

@@

```{r}
rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Bat Lives",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Bat Lives",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Bryant|deGrom|Bumgarner|Devers",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Painting",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Poofer",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Bregman|Walker|deGrom|Lindor",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Painting",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Santana|Robertson|deGrom|Devers",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```
```{r}
rosters_with_adj_projections %>% 
  filter(grepl("Free Agent|Plouffe",team),
         grepl("RP",display_position)) %>% 
  ggplot(aes(x=team,y=zar)) +
  geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

@@

>>>>

```{r}
# check if file exists, maybe move all in this chunk to a script
filename <- function(name) {
  paste0("data/",name,"_",gsub("-","",Sys.Date()),".Rds")
}

draft_results <- read_tsv("data/draftResults.tsv") %>% 
  clean_names() %>% 
  mutate(player = stri_trans_general(player, "latin-ascii"),
           round = ceiling(pick/12)) %>%  
  select(player, pick, round) %>% 
  rename(draft_pick = pick,
         draft_round = round)

@@

```{r}
# TODO find way to wrap these three views into one
rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Poofer",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Poofers",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Poofer",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Bregman|deGrom|Lindor",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```

```{r}
rosters_with_adj_projections %>% 
  filter(!grepl("Free Agent",team),
         grepl("SP|3B",display_position)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

@@

```{r}
#TODO measuring projected value of draft picks, move to separate research
rosters_with_adj_projections %>% 
  filter(!is.na(draft_pick)) %>% 
  group_by(draft_round) %>% 
  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
  ggplot(aes(x=draft_round,y=zar_mean)) +
  geom_col() +
  geom_line(aes(y=zar))

rosters_with_adj_projections %>% 
  filter(!is.na(draft_pick)) %>% 
  group_by(draft_round) %>% 
  arrange(draft_round) %>% 
  ggplot(aes(x=draft_round,y=zar,group=draft_round)) +
  geom_boxplot()
```
